---
title: "Homework 1"
author: Pallavi Krishnamurthy
output: html_document
---

This is my solution to Homework 1 

```{r lib_calls}
library(tidyverse)
```

# problem 1 

## Part 1 :

Create a data frame with specified elements 
-a random sample of size 10 from a standard Normal distribution
-a logical vector indicating whether elements of the sample are greater than 0
-a character vector of length 10
-a factor vector of length 10, with 3 different factor “levels”

```{r dataframe}
prob1_df =
tibble(
  samp = rnorm(10),
  samp_gt_0 = samp > 0, 
  char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  factor_vec = factor(c("low","low", "low", "mod", "mod", "mod", "high", "high", "high", "high"))
)
```

Take the mean of each variable in the data frame prob1_df.

```{r dataset_mean}
mean(pull(prob1_df, samp)) 
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

Answer - The mean of a random sample of size 10 from a standard Normal distribution and the logical vector greater than zero gives a numeric result that is correct. However, the mean of the character vector and factor vector does not give a numeric results because it does not make sense to take the mean of "a", "b", "c", ... or "low", "mod" and "high". Hence, R gives a warning message that the argument if not numeric or logical : returning NA (Not Applicable). 

Explicitly convert variables from one type to another. Here we convert variables to numeric type. 

```{r covert_type_1, warning=FALSE, results='hide'}
as.numeric(pull(prob1_df, samp)) 
as.numeric(pull(prob1_df, samp_gt_0)) 
as.numeric(pull(prob1_df, char_vec)) 
as.numeric(pull(prob1_df, factor_vec)) 
```

Answer - The results for character vector is still not applicable. This is correct. The results for factor variable
now yields a numeric value. This is because R forces the factor vector to take a numeric value when we explicitly change the variable type to numeric. We have to be cautious while changing types to make sure the results make sense. 

